Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/intro.tex
Fix a few figure references.

There is, however, a difference to be detected.  The bottom panels of Figure~\ref{}fig:introexample} show, for each respective simulation, parameters (as discussed in Section~\ref{}) governing the tendency towards reciprocation for members of each group vis a vis communications coming from in- or out-group members.  For both simulated cases, the log-hazard for an event in which a member of group A or group B immediately responds to an incoming communication from an in-group member is increased by an increment of 2 (relative to a non-reciprocating event), and the log-hazard for an event in which a member of group B immediately responds to an incoming communication from a member of group A is increased by a corresponding increment of 0.5.  Groups A and B are thus distinctive in terms of their dynamic behavior, even in the absence of marginal differences in propensity to communicate.  A blockmodeling approach that classifies nodes based on shared dynamics (rather than merely shared marginal communication rates) can potentially identify such subtle distinctions; in this paper, we introduce such an approach.

>>>>

There is, however, a difference to be detected.  The bottom panels of Figure~\ref{fig:introexample} show, for each respective simulation, parameters (as discussed in Section~\ref{sec:specification}) governing the tendency towards reciprocation for members of each group vis a vis communications coming from in- or out-group members.  For both simulated cases, the log-hazard for an event in which a member of group A or group B immediately responds to an incoming communication from an in-group member is increased by an increment of 2 (relative to a non-reciprocating event), and the log-hazard for an event in which a member of group B immediately responds to an incoming communication from a member of group A is increased by a corresponding increment of 0.5.  Groups A and B are thus distinctive in terms of their dynamic behavior, even in the absence of marginal differences in propensity to communicate.  A blockmodeling approach that classifies nodes based on shared dynamics (rather than merely shared marginal communication rates) can potentially identify such subtle distinctions; in this paper, we introduce such an approach.
